\vspace{-2cm} Inference on the Effects of Observed Features \\ in Latent Space Models for Networks

### 2016-08-31 manuscript.tex
added yet another quote, from cao2016transnational

Likewise, similar claims are made in \citet{dorff2013networks, cao2013democracies, ward2013gravity, kirkland2012multimember}.

@@

The above examples are drawn from political science, but we see a similar logic for using the LSM articulated in recent work in ecology by \citet[p. 989]{nomano2015unrelated}.

>>>>

Likewise, similar claims are made in \citet{dorff2013networks, cao2013democracies, ward2013gravity, kirkland2012multimember}, and \citet{cao2016transnational}.

@@

\begin{quote}
``Ignoring third-order dependence in dyadic data and treating dyads Germany-France, France-Italy, and Germany-Italy as independent observations can cause bias in parameter estimates (Hoff 2005). The statistical literature has proposed a series of latent space to control for autocorrelation among dyadic observations (Hoff et al. 2002; Hoff 2005). Countries? unobserved characteristics are captured by latent vectors...'' \citep[p. 17]{cao2016transnational}.
\end{quote}

The above examples are drawn from political science, but the results of our analysis have implications in other fields. We see a similar logic for using the LSM articulated in recent work in ecology by \citet[p. 989]{nomano2015unrelated}.
